---
title: "FSU-KNU Hackathon Analysis"
author: "Bret Staudt Willet"
date: "2024-12-05"
output:
  html_document: default
  pdf_document: default
---

**Published output:** https://rpubs.com/bretsw/hackathon-fsu-knu-2024

**Source code:** https://github.com/bretsw/hackathon-fsu-knu-2024

```{r setup, message=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


```{r, message=FALSE, include=FALSE}
df <- 
  read_csv("FSU KNU hackathon - Fall 2024.csv") %>% 
  rename(
    participant_id = "Response ID",
    country = "Country",
    team = "Which team were you on? (Please enter your team name.)",
    hackathon_xp = "Not counting this event, how many times have you previously participated in hackathons or similar events? - 1",
    international_xp = "Have you participated previously in international group projects?",
    fav_programming = "What is your favorite programming language/stack? - Selected Choice",
    event_organization = "How well was this event organized?",
    event_satisfaction = "How satisfied are you with this event?",
    sdl_goals = "Please rate the degree to which you agree with the following statements about your participation in the event: - I set goals for myself while problem-solving during the event.",
    sdl_evaluation = "Please rate the degree to which you agree with the following statements about your participation in the event: - I took time to evaluate my progress toward those goals.",
    sdl_outside_sources = "Please rate the degree to which you agree with the following statements about your participation in the event: - I sought new information, resources, knowledge during the event.",
    sdl_practice = "Please rate the degree to which you agree with the following statements about your participation in the event: - I practiced new skills during the event.",
    sdl_satisfaction = "Please rate the degree to which you agree with the following statements about your participation in the event: - I am happy with my problem-solving processes during the event.",
    intercultural_skills = "Please rate the degree to which you agree with the following statements about your participation in the event: - I developed my intercultural communication skills during this event.",
    intercultural_knowledge = "Please rate the degree to which you agree with the following statements about your participation in the event: - I learned new information about a foreign country and culture through this event.",
    intercultural_comfortability = "Please rate the degree to which you agree with the following statements about your participation in the event: - I feel comfortable working in international and multicultural group projects after this event.",
    support_past_knowledge = "Please rate the importance of the following supports for problem-solving during this event: - Past knowledge and existing skills",
    support_event_teammates = "Please rate the importance of the following supports for problem-solving during this event: - Event teammates",
    support_event_experts = "Please rate the importance of the following supports for problem-solving during this event: - Event experts",
    support_outside_friends = "Please rate the importance of the following supports for problem-solving during this event: - Friends and colleagues not participating in the event",
    support_social_media = "Please rate the importance of the following supports for problem-solving during this event: - Social media and web forums",
    support_books = "Please rate the importance of the following supports for problem-solving during this event: - Textbooks, guidebooks, manuals, etc.",
    support_ai = "Please rate the importance of the following supports for problem-solving during this event: - Generative AI tools (e.g., ChatGPT, Copilot, Gemini, Claude, etc.)",
    helpfulness_event_experts = "How helpful were the event experts?",
    career_forward = "Are you ready to move forward in your career?",
    career_preparedness = "Please rate, with 1 being not at all prepared and 10 being completely prepared, the degree to which you feel ready to move forward in your career because of this event: - 1",
    future_involvement = "Would you be interested in participating in a future international event like this (e.g., hackathon, design sprint)?",
    description_overall = "Briefly describe your overall impressions of this event:",
    description_learning = "Briefly describe two or more new things you learned about your international partners through this binational event."
  ) %>%
  mutate(participant = row_number()) %>%
  select(participant, everything())
```


```{r, include=FALSE, eval=FALSE}
names(df)
```


```{r, include=FALSE}
df_longer <-
  df %>%
  pivot_longer(
    cols = starts_with("sdl"),
    names_to = "sdl_category",
    values_to = "sdl_rating"
  ) %>%
  pivot_longer(
    cols = starts_with("support"),
    names_to = "support_category",
    values_to = "support_rating"
  ) %>%
  pivot_longer(
    cols = starts_with("intercultural"),
    names_to = "intercultural_category",
    values_to = "intercultural_rating"
  ) %>%
  mutate(
    sdl_factor = factor(sdl_rating),
    support_factor = factor(support_rating),
    intercultural_factor = factor(intercultural_rating)
  )
```


```{r, include=FALSE, eval=FALSE}
glimpse(df_longer)
```


---

## Self-Directed Learning

### Please rate the degree to which you agree with the following statements about your participation in the event:

```{r, include=FALSE}
df_sdl_category <-
  df_longer %>%
  distinct(participant, sdl_category, .keep_all = TRUE) %>% 
  mutate(sdl_category = 
           str_replace_all(sdl_category, 
                           c("sdl_goals" = "I set goals for myself while problem-solving during the event.",
                             "sdl_evaluation" = "I took time to evaluate my progress toward those goals.",
                             "sdl_outside_sources" = "I sought new information, resources, knowledge during the event.",
                             "sdl_practice" = "I practiced new skills during the event.",
                             "sdl_satisfaction" = "I am happy with my problem-solving processes during the event."
                           )
           )
  )
```

```{r, echo=FALSE}
df_sdl_category %>% 
  group_by(sdl_category) %>%
  summarize(sdl_mean = mean(sdl_rating, na.rm = TRUE)) %>%
  arrange(desc(sdl_mean)) %>%
  mutate(sdl_mean = round(sdl_mean, 3)) %>%
  rename("Self-Directed Learning Enactment" = sdl_category,
         "Mean Score (1-10)" = sdl_mean)
```

```{r, echo=FALSE, out.width="100%"}
df_sdl_category %>%
  ggplot(aes(x = sdl_category, fill = sdl_factor)) +
  geom_bar() +
  labs(title = "Self-Directed Learning Enactment",
       x = NULL,
       y = "Count") +
  coord_flip() +
  theme_bw()  +
  theme(axis.text.y = element_text(angle = 15))
```


### Please rate the importance of the following supports for problem-solving during this event:

```{r, include=FALSE}
df_sdl_support <-
  df_longer %>%
  distinct(participant, support_category, .keep_all = TRUE) %>% 
  mutate(support_category = 
           str_replace_all(support_category, 
                           c("support_past_knowledge" = "Past knowledge and existing skills",
                             "support_event_teammates" = "Event teammates",
                             "support_event_experts" = "Event experts",
                             "support_outside_friends" = "Friends and colleagues not participating in the event",
                             "support_social_media" = "Social media and web forums",
                             "support_books" = "Textbooks, guidebooks, manuals, etc.",
                             "support_ai" = "Generative AI tools (e.g., ChatGPT, Copilot, Gemini, Claude, etc.)"
                           )
           )
  )
```

```{r, echo=FALSE}
df_sdl_support %>%
  group_by(support_category) %>%
  summarize(support_mean = mean(support_rating, na.rm = TRUE)) %>%
  arrange(desc(support_mean)) %>%
  mutate(support_mean = round(support_mean, 3)) %>%
  rename("Importance of Self-Directed Learning Supports" = support_category,
         "Mean Score (1-10)" = support_mean)
```

```{r, echo=FALSE, out.width="100%"}
df_sdl_support %>%
  ggplot(aes(x = support_category, fill = support_factor)) +
  geom_bar() +
  labs(title = "Self-Directed Learning Supports",
       x = "",
       y = "Count") +
  coord_flip() +
  theme_bw() +
  theme(axis.text.y = element_text(angle = 15))
```



---

## Intercultural Experience

### Please rate the degree to which you agree with the following statements about your participation in the event:

```{r, include=FALSE}
df_intercultural <-
  df_longer %>%
  distinct(participant, intercultural_category, .keep_all = TRUE) %>% 
  mutate(intercultural_category = 
           str_replace_all(intercultural_category, 
                           c("intercultural_skills" = "I developed my intercultural communication skills.",
                             "intercultural_knowledge" = "I learned new information about a foreign country and culture.",
                             "intercultural_comfortability" = "I feel comfortable working in international and multicultural group projects."
                           )
           )
  )
```

```{r, echo=FALSE}
df_intercultural %>%
  group_by(intercultural_category) %>%
  summarize(intercultural_mean = mean(intercultural_rating, na.rm = TRUE)) %>%
  arrange(desc(intercultural_mean)) %>%
  mutate(intercultural_mean = round(intercultural_mean, 3)) %>%
  rename("Intercultural Experience" = intercultural_category,
         "Mean Score (1-10)" = intercultural_mean)
```

```{r, echo=FALSE, out.width="100%"}
df_intercultural %>%
  ggplot(aes(x = intercultural_category, fill = intercultural_factor)) +
  geom_bar() +
  labs(title = "Intercultural Experience",
       x = "",
       y = "Count") +
  coord_flip() +
  theme_bw()  +
  theme(axis.text.y = element_text(angle = 15))
```



---

## Event Evaluation

### How satisfied are you with this event?

```{r, echo=FALSE}
df %>%
  mutate(event_satisfaction = 
           factor(event_satisfaction, 
                  levels = c("Absolutely pleased. When will the next one be?", 
                             "Satisfied", 
                             "Dissatisfied"
                  )
           )
  ) %>%
  count(event_satisfaction) %>%
  rename("Satisfaction with Event" = event_satisfaction,
         "Number of Responses" = n)
```


### How well was this event organized?

```{r, echo=FALSE}
df %>%
  mutate(event_organization = factor(event_organization, 
                                     levels = c("Perfectly", "Good", "Not bad", "Badly", "Terribly"))
         ) %>%
  count(event_organization) %>%
  bind_rows(
    tibble(
      event_organization = "Terribly",
      n = 0
    )
  ) %>%
  rename("Organization of Event" = event_organization,
         "Number of Responses" = n)
```


### How helpful were the event experts?

```{r, echo=FALSE}
df %>%
  mutate(helpfulness_event_experts = 
           factor(helpfulness_event_experts, 
                  levels = c("Super helpful", 
                             "Useful", 
                             "Enough",
                             "Did not help",
                             "I did not follow their recommendations",
                             "I am an expert"
                  )
           )
  ) %>%
  count(helpfulness_event_experts) %>%
  bind_rows(
    tibble(
      helpfulness_event_experts = 
        c("Did not help", 
          "I did not follow their recommendations",
          "I am an expert"
        ), 
      n = c(0, 0, 0)
    )
  ) %>%
  filter(!is.na(helpfulness_event_experts)) %>%
  rename("Helpfulness of Experts" = helpfulness_event_experts,
         "Number of Responses" = n)
```


### Are you ready to move forward in your career?

```{r, echo=FALSE}
df %>%
  count(future_involvement) %>%
  rename("Ready to Move Forward" = future_involvement,
         "Number of Responses" = n)
```


### Please rate, with 1 being not at all prepared and 10 being completely prepared, the degree to which you feel ready to move forward in your career because of this event: 

```{r, echo=FALSE}
df %>%
  count(career_preparedness) %>%
  bind_rows(
    tibble(
      career_preparedness = c(2, 5),
      n = c(0, 0)
    )
  ) %>%
  arrange(career_preparedness) %>%
  rename("Readiness to Move Forward" = career_preparedness,
         "Number of Responses" = n)
```



---

## Participant Background

### Not counting this event, how many times have you previously participated in hackathons or similar events? 

```{r, echo=FALSE}
df %>%
  count(hackathon_xp) %>%
  bind_rows(
    tibble(
      hackathon_xp = c(2, 4, 7, 8 , 9, 10),
      n = c(0, 0, 0, 0, 0, 0)
    )
  ) %>%
  arrange(hackathon_xp) %>%
  rename("Number of Past Hackathons" = hackathon_xp,
         "Number of Responses" = n)
```


### Have you participated previously in international group projects?

```{r, echo=FALSE}
df %>%
  count(international_xp) %>%
  rename("Past International Group Projects" = international_xp,
         "Number of Responses" = n)
```


### What is your favorite programming language/stack?

```{r, echo=FALSE}
df %>%
  count(fav_programming) %>%
  bind_rows(
    tibble(
      fav_programming = c("R", "PHP"), 
      n = c(0, 0)
    )
  ) %>%
  arrange(desc(n)) %>%
  rename("Favorite Programming Language" = fav_programming,
         "Number of Responses" = n)
```
